Reliable Inferences from Simply Parameterised Models

### 2012-08-07 ms.tex
Small tweaks

\title{Robust Inferences from Simply Parameterised Models}

@@

\item $p(D|\theta)$ is a function of
both $\theta$ and $D$ and is referred to as the {\it sampling distributions}. 
The reason for the awkward plural is that $p(D|\theta)$ is a set of probability distributions,
one for each value of $\theta$. The sampling distributions describe our prior information about how the data are connected to the parameters \citep{2008arXiv0808.0012C}. \\

\item $p(D|\theta)|_{D = D_{\rm obs}}$ is called the {\it likelihood function}.
It is obtained from the sampling distributions, with the actual data substituted in,
and is therefore a function of $\theta$ only. It describes the effects of the actual data
set that was observed on our beliefs about $\theta$: values of $\theta$ with a high
likelihood predicted the data well and will have their probability upweighted
in the posterior distribution.
\end{itemize}

@@

\section{Advantages and Disadvantages of Simply Parameterised Models}
\begin{itemize}
\item Easy to implement \\
\item Computationally fast to get inferences - therefore can be applied on a large scale, e.g. to large samples of objects. \\
\item Easy to assign non-controversial priors over low dimensional parameter spaces \\
\end{itemize}

@@

\section*{Acknowledgements}
Tommaso Treu, Anna Pancoast, Phil Marshall, Matthew Auger, Greg Dobler, Sebastian Hoenig

>>>>

\title{Reliable Inferences from Simply Parameterised Models}

@@

\item $p(D|\theta)$ is a function of
both $\theta$ and $D$ and is referred to as the {\it sampling distribution}. 
The sampling distribution $p(D|\theta)$ is a set of probability distributions,
one for each value of $\theta$, and describe our prior information about how the data are connected to the parameters \citep{2008arXiv0808.0012C}.

\item $p(D|\theta)|_{D = D_{\rm obs}}$ is called the {\it likelihood function}.
It is obtained from the sampling distribution, with the actual data substituted in,
and is therefore a function of $\theta$ only. It describes the effects of the actual data
set that was observed on our beliefs about $\theta$: values of $\theta$ with a high
likelihood predicted the data well and will have their probability upweighted
in the posterior distribution.
\end{itemize}

@@

\section{The Failure of Simply Parameterised Models}
\begin{itemize}
\item Easy to implement \\
\item Computationally fast to get inferences - therefore can be applied on a large scale, e.g. to large samples of objects. \\
\item Easy to assign non-controversial priors over low dimensional parameter spaces \\
\end{itemize}

@@

\section*{Acknowledgements}
Tommaso Treu, Anna Pancoast, Phil Marshall, Matthew Auger, Greg Dobler, Sebastian Hoenig, Douglas Applegate
